Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-22 manuscript/common_latex.tex
add optional argument for FPKM cutoff

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by FPKM less than 1
  were excluded from the plotted tree. Heatmap cells in white are from
  species where there was no expression of the relevant transcript (or
  a species where that transcript does not apply). The species names
  are abbreviated with the first letter of the genus and first two
  letters of the species (for example, \textit{Homo sapiens} is
  \textit{H.sa.}). Genes with duplicate gene names in the same species
  (or no gene named defined) are listed by the Ensemble gene ID.}

>>>>

\newcommand{\genetreeexplanation}[2][1]{Gene tree and heatmap of
  expression of genes related to #2. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by FPKM less than #1
  were excluded from the plotted tree. Heatmap cells in white are from
  species where there was no expression of the relevant transcript (or
  a species where that transcript does not apply). The species names
  are abbreviated with the first letter of the genus and first two
  letters of the species (for example, \textit{Homo sapiens} is
  \textit{H.sa.}). Genes with duplicate gene names in the same species
  (or no gene named defined) are listed by the Ensemble gene ID.}
